Using forecasting models for new book publishing

### 2015-07-22 paper.tex
traduciendo

% La industria editorial se basa en varios pasos y procesos productivos / La publicación de un libro requiere de varios pasos / Además, la distribución es importante y juega un papel importante
The publishing industry is based on very particular and established production processes, and publishing a book requires several steps, between whom the distribution is important and plays an important role.

% Esos pasos hacen que el proceso y las decisiones individuales en cada paso sean muy importantes. Una de esas decisiones es el número de ejemplares a imprimir.
The publishing process and individual decisions at each step are very important. One of those decisions is the number of copies to print.

@@

% El uso de herramientas de predicción puede ser beneficioso para una empresa editorial para optimizar la producción y así mejorar sus ganancias o minimizar pérdidas \cite{Zhao2001}. Un ejemplo es la optimización de las ventas \cite{Mattila2002}, mejorando el margen de ganancia al vender toda la tirada editorial.

%---------- estado del arte

@@

%---------- final de la intro

El resto del paper está organizado como sigue...

%********************************************************************************
\section{The problem}

%********************************************************************************
\section{Methodology}

@@

%********************************************************************************
\section{Experiments and Results}

%********************************************************************************
\section{Conclusions and Future Work}

>>>>

% La industria editorial se basa en varios pasos y procesos productivos / La publicación de un libro requiere de varios pasos / Además, la distribución es importante y juega un papel importante
In this sense, the publishing industry is based on very particular and established production processes, and publishing a book requires several steps, between whom the distribution is important and plays an important role.
% Esos pasos hacen que el proceso y las decisiones individuales en cada paso sean muy importantes. Una de esas decisiones es el número de ejemplares a imprimir.
The publishing process and individual decisions at each step are very important. One of those decisions is the number of copies to print.

@@

% El uso de herramientas de predicción puede ser beneficioso para una empresa editorial para optimizar la producción y así mejorar sus ganancias o minimizar pérdidas \cite{Zhao2001}. Un ejemplo es la optimización de las ventas \cite{Mattila2002}, mejorando el margen de ganancia al vender toda la tirada editorial.
Using predictive tools can benefit a publishing company to optimize production and improve their profits or minimize losses \cite{Zhao2001}. 
An example is the optimization of sales \cite{Mattila2002} by improving profit margins by selling the whole publishing roll.

\bigskip
%---------- estado del arte

@@

\bigskip
%---------- final de la intro

The rest of this paper is structured as follows:
%Section \ref{sec:soa} presents a comprehensive review of the approaches found in the bibliography to BLA BLA BLA.
Section \ref{sec:methodology} briefly describes the EA algorithm, and analyzes the parameters we propose to evaluate.
This section also presents the experimental setup and the methodology considered in the study. 
Section \ref{sec:experiments} details the statistical study based on ANOVA. 
Obtained results are analyzed in order to establish the most suitable values.
Finally, conclusions and future work are presented in Section \ref{sec:conclusionsAndFutureWork}.

%********************************************************************************
\section{The problem}
\label{sec:problem}

%********************************************************************************
\section{Methodology}
\label{sec:methodology}

@@

%********************************************************************************
\section{Experiments and Results}
\label{sec:experiments}

aquí hay que contar los experimentos realizados y presentar los resultados obtenidos

%********************************************************************************
\section{Conclusions and Future Work}
\label{sec:conclusionsAndFutureWork}
